Dark Control:\\ A Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-09-17 paper/paper.tex
Update of Fig 3 w/ Bellman equation

\subsection{Markov decision processes}
Model-free RL has had great success in many real-world problems,
including robotics \citep{ng2004,abbeel2004},
super-human performance in complex video games \citep{mnih2015},
and strategic board games like the breakthrough results upon recently on the game of Go \citep{silver2016mastering}, considered to be a golden benchmark problem in artificial intelligence.
We emphasize that the brain in general, and the DMN in particular,
is a physical system governed by the laws of
physics and can be formally described
by Markov processes at a sufficiently coarse scale.
It has indeed been previously proposed \citep{tegmark2016improved} that
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.
\begin{wrapfigure}{l}{.4\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{rl.pdf}
  \caption{\textbf{Reinforcement learning in a nutshell.} Given the current state of the environment,
    the agent takes an action by following some policy, receives a consequential reward and observes the next state. The process goes on until interrupted or a goal state is reached.}
  \label{fig:rl}
\end{wrapfigure}
% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.

>>>>

\subsection{Markov decision processes}
Model-free RL has had great success in many real-world problems,
including robotics \citep{ng2004,abbeel2004},
super-human performance in complex video games \citep{mnih2015},
and strategic board games like the breakthrough results upon recently on the game of Go \citep{silver2016mastering}, considered to be a golden benchmark problem in artificial intelligence.
We emphasize that the brain in general, and the DMN in particular,
is a physical system governed by the laws of
physics and can be formally described
by Markov processes at a sufficiently coarse scale.
It has indeed been previously proposed \citep{tegmark2016improved} that
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.
\begin{wrapfigure}{l}{.4\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{rl2.pdf}
  \caption{\textbf{Reinforcement learning in a nutshell.} Given the current state of the environment,
    the agent takes an action by following the policy matrix as updated by the Bellman equation. The agent receives a consequential reward and observes the next state. The process goes on until interrupted or a goal state is reached.}
  \label{fig:rl}
\end{wrapfigure}
% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
